---
title: "dataset con la información de las paradas de metro de Madrid"
author: "Team Taquito"
date: "10/6/2021"
output: html_document
runtime: shiny
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = FALSE)
```

## Informacion de paradas de metro de Madrid

El lugar de donde se toma la información para analizar el Dataset relacionado con las paradas más relevantes dentro de Madrid provienen de la siguiente página:
<https://www.adictosaltrabajo.com/2019/10/30/leer-un-json-con-r-rstudio/>.

Lo primero que nosotros vamos a realizar será las peticiones API al servidor que contienen la información y algo muy importante es que las peticiones API las podemos hacer igual que una query SQL, pero en lugar de tener como resultado una dupla lo que vamos a tener es un archivo JSON. Esto permitiría cubrir los apartados de bases SQL Y JSON.
La API correspondientes base:
<https://idealista.carto.com:443/api/v2/sql?/>.

```{r, include=FALSE}
  library(jsonlite)
  library(curl)
  library(tidyverse)
```


```{r, echo=TRUE}
q <- curl_escape("select ID, NAME, LINE, PLACE, LAT, LNG from public.paradas_metro_madrid")
uri_paradas_metro <- paste("https://idealista.carto.com/api/v2/sql?q=",q, sep="")
paradas_metro <- fromJSON(uri_paradas_metro)
paradas_metro <- paradas_metro[["rows"]]
```


```{r, echo=TRUE}
inputPanel(
  selectInput("n_breaks", label = "Station:",
              choices = c("L1","L2","L3","L4","L5","L6","L6","L7","L8","L9","L10"), selected = "L2")
)

renderTable({paradas_metro%>%filter(line==input$n_breaks)})

```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



